---
title: "Quantitative and Qualitative Data Visualization"
author: Faisal Mustafa,
date: November 7, 2025 (Updated on `r format(Sys.Date(), '%B %d, %Y')`)
output: 
  github_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quantitative Data Visualization

### Factor Analysis

## Qualitative Data Visualization

### WordCoud

WordCloud can be used to dhow the trend in the data. For this purpose, let's use the data that from ......

```{r cache= TRUE}
df_wordcloud <- read.csv("https://faisalmustafa.github.io/data_visualization/data/nguyen2026.csv")
```

```{r cache= TRUE}
head(df_wordcloud)
```

Next, let's create a frequency table based on the data, and remove record containing *Not Applicable*.

```{r results='hide', message=FALSE, warning=FALSE, cache = TRUE}
library(dplyr)
tb <- as.data.frame(table(df_wordcloud$Term)) %>% 
  filter(Var1 != "Not Applicable")
```

```{r cache= TRUE}
head(tb)
```

Now we are ready to create a Word Cloud based on the data. In this instance, let's use ```wordcloud``` package.

```{r results='hide', message=FALSE, warning=FALSE, cache= TRUE}
library(wordcloud)
```

```{r echo=TRUE, cache= TRUE}
wordcloud(words = tb$Var1 , freq = tb$Freq, scale=c(2,0.2), min.freq = 1,
          max.words=100, random.order=FALSE, rot.per=0.35,
          colors= RColorBrewer::brewer.pal(8, "Dark2"))
```

To save the image into a file (e.g., PNG) and adjust its size and resolution, enclose the above code with two lines below:


```{r eval=FALSE}
png(filename="wordcloud.png", width=30, height=30, units="cm", res = 600)

wordcloud(words = tb$Var1 , freq = tb$Freq, scale=c(2,0.2), min.freq = 1,
          max.words=100, random.order=FALSE, rot.per=0.35,
          colors= RColorBrewer::brewer.pal(8, "Dark2"))

dev.off()
```

### Linking Demographic Informatic with a Bipartite Chart



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.